\documentclass[10pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\section{Ryan Breed}\label{ryan-breed}

\begin{longtable}[]{@{}ll@{}}
\toprule
Contact & Info\tabularnewline
\midrule
\endhead
email &
\href{mailto:recruit@REMOVETHIS.breed.org}{\texttt{recruit@breed.org}}\tabularnewline
voice &
\href{tel:+16617273331}{\texttt{+1\ (661)RBR-EED1}}\tabularnewline
github &
\href{https://github.com/ryanbreed}{\texttt{github.com/ryanbreed}}\tabularnewline
linkedin &
\href{https://www.linkedin.com/in/ryanbreed}{\texttt{linkedin.com/in/ryanbreed}}\tabularnewline
\bottomrule
\end{longtable}

\subsection{Overview}\label{overview}

Seasoned security professional with 19 years of deep technical
experience in security assessment, penetration testing, security
monitoring, incident response, application security, and security
architecture. I have a keen interest in practical applications of
large-scale data analysis and infrastructure automation to increase
organizational resilience to cyber attacks and other major disturbances.
I also have practical experience automating Cyber Threat Intelligence
sharing and organizing collective security initiatives through
cooperative information sharing with public and private sector entities.

\subsection{Education}\label{education}

\begin{itemize}
\tightlist
\item
  University of Texas at Austin LBJ School of Public Affairs - Global
  Policy Studies (2012--2014)
\item
  University of Rochester - Bachelor of Science in Molecular Genetics
  (1997)
\end{itemize}

\subsection{Experience}\label{experience}

\subsubsection{Principal, Critical Infrastructure
Security}\label{principal-critical-infrastructure-security}

\subparagraph{\texorpdfstring{\emph{Electric Reliability Council of
Texas (ERCOT)} (Nov 2012 - Oct
2016)}{Electric Reliability Council of Texas (ERCOT) (Nov 2012 - Oct 2016)}}\label{electric-reliability-council-of-texas-ercot-nov-2012---oct-2016}

\begin{itemize}
\tightlist
\item
  Individual contributor responsible for engaging business units to
  develop strategic opportunities for improving grid and market systems
  while delivering on key security initiatives.
\item
  Serve as senior resource in critical security incidents by directing
  tasking and providing investigation and analytical support as
  necessary.
\item
  Develop novel analytics for security event data. Exploit home-field
  advantage to degrade adversarial mobility and freedom of action.
\item
  Prioritize intelligence collection and analysis projects. Develop
  strategic plans for threats to critical grid and market systems.
\item
  Research and implement emerging technologies for application to
  business and security challenges.
\item
  Perform outreach to public and private sector via ISO/RTO council and
  DHS CISCP. Engage in public speaking to advocate for electricity
  sector needs and share information and practices
\end{itemize}

\subparagraph{Accomplishments}\label{accomplishments}

\begin{itemize}
\tightlist
\item
  Automated real-time integration of CMDB, IPAM, access control, and
  vulnerability data into machine-readable representation of entities,
  applications, business systems, and infrastructure.
\item
  Automated defensive countermeasures. Used model data to safely deploy
  automated containment, investigation, and other response
  countermeasures in response to automated threat detection analytics.
\item
  Implemented TAXII endpoint to ingest STIX cyber threat intelligence
  feeds and propagate indicators to monitoring and control surfaces.
\item
  Developed security testing for Continuous Integration. Used Bamboo to
  automate Nexpose for vulnerability and baseline assessment. Security
  findings over a project-specific risk threshold triggered a build
  failure and intiated response notification chain.
\item
  Developed automated report and security finding distribution.
  Management reports were automatically updated and reconfigured based
  on changes to underlying assets and changes in responsible parties.
\item
  Developed Ansible playbooks for CIS benchmarks and Nexpose
  vulnerabilities. Automated compliance artifact creation and
  remediation of findings in dev/test environments. Tickets for specific
  findings were dispatched to responsible parties where human
  intervention was required.
\item
  Implemented ELK stack for monitoring BroIDS, auditd, RSA Netwitness,
  and ArcSight ESM/Connector logs. Developed custom logstash plugins to
  enable event ingest from CMDB and ArcSight.
\item
  Implemented Telegraf, InfluxDB, and Grafana to translate event data
  into time series domain for tracking metrics and developing new
  analytics. Collected system telemetry with telegraf to enable
  performance analysis.
\item
  Developed scenario and training injects for GridEx III. Developed
  cyber simulator and ChatOps platform for use during exercise play.
\item
  Developed Big Data test bed. Deployed DataStax Enterprise Cassandra,
  Hortonworks Hadoop, Apache Spark, GraphLab, Neo4j, and JupyterHub
  environments loaded with data from IT, market, and grid systems.
  Developed proof-of-concept analyses showcasing each technology
  platform for evaluation by business and IT owners
\end{itemize}

\subsubsection{Manager, Critical Infrastructure
Security}\label{manager-critical-infrastructure-security}

\subparagraph{\texorpdfstring{\emph{Electric Reliability Council of
Texas (ERCOT)} (Dec 2009 - Nov
2012)}{Electric Reliability Council of Texas (ERCOT) (Dec 2009 - Nov 2012)}}\label{electric-reliability-council-of-texas-ercot-dec-2009---nov-2012}

\begin{itemize}
\tightlist
\item
  Managed a team of 9 security analysts to cover security operations,
  monitoring, incident response, compliance controls, and security
  architecture.
\item
  Managed departmental budget, including annual and quarterly
  forecasting. Developed and presented project proposals for cyber
  security initiatives.
\item
  Provided guidance and oversight in the capital project process to
  ensure security objectives were incorporated into investment
  initiatives.
\item
  Lead audit response efforts for cyber security control activities in
  NERC CIP and SAS70 compliance programs.
\item
  Managed tasking and tracking to remediate findings from audits and
  other outside assessments.
\item
  Managed employee performance and aligned career development goals with
  strategic department objectives.
\item
  Developed working threat model for market and grid operations to guide
  strategic planning.
\item
  Developed, maintained, and exercised Disaster Recovery and Business
  Continuity plans for cyber security systems.
\item
  Contracted outside penetration tests and assessments to proactively
  identify and remediate security issues in business and IT systems.
\item
  Lead participation in public/private partnership projects with DOE and
  DHS.
\item
  Attained SECRET clearance under DHS Private Sector Clearance Program
  and attended threat briefings as necessary.
\end{itemize}

\subparagraph{Accomplishments}\label{accomplishments-1}

\begin{itemize}
\tightlist
\item
  Led implementation of DOE ESNM/CRISP pilot site and participated in
  program development workshops.
\item
  Developed automated security advisory analysis system to triage,
  score, and dispatch vendor advisories and vulnerability notifications.
\item
  Represented Cybersecurity Department in GridEx II Exercise Play.
\item
  Represented Electricity Subsector in classified threat workshops for
  IC at DOE INL.
\end{itemize}

\subsubsection{Lead, Security
Operations}\label{lead-security-operations}

\subparagraph{\texorpdfstring{\emph{Electric Reliability Council of
Texas (ERCOT)} (Dec 2005 - Dec
2009)}{Electric Reliability Council of Texas (ERCOT) (Dec 2005 - Dec 2009)}}\label{electric-reliability-council-of-texas-ercot-dec-2005---dec-2009}

\begin{itemize}
\tightlist
\item
  Performed security monitoring, incident response, and investigations.
\item
  Infrastructure design and implementation for SIEM, IPS, IDS,
  Enterprise Forensics, full-content packet capture, web content
  filtering, and vulnerability management.
\item
  Workflow development for security operations, monitoring, and
  investigation processes. Developed dashboards, reports, and incident
  documentation templates. Documented procedures and created reports for
  compliance controls.
\item
  SIEM content development for automated analysis of security events.
\item
  IDS/IPS signature development to incorporate cyber observables
  extracted from investigations into real-time monitoring functions.
\item
  Perform forensic analysis of incident artifacts and other digital
  evidence. Develop incident reports and brief management on findings
  and recommended response actions
\end{itemize}

\subparagraph{Accomplishments}\label{accomplishments-2}

\begin{itemize}
\tightlist
\item
  Deployed 2 major iterations of ArcSight ESM
\item
  Integrated ArcSight ESM with IBM/ISS IPS, Snort NIDS, Tenable Nessus,
  Windows Events, UNIX/Network/Firewall Syslog, Oracle RDBMS, Microsoft
  SQL Server and Symantec Antivirus.
\item
  Developed automated analysis tools for decoding malicious javascript
  extracted from network traffic.
\item
  Developed full-content packet capture and indexing system to extract
  packet captures indexed on time and IP address.
\item
  Developed management application for BlueCoat site categorization via
  local policy database
\end{itemize}

\subsubsection{Security Consultant}\label{security-consultant}

\subparagraph{\texorpdfstring{\emph{Unisys} (Mar 2003 - Dec
2005)}{Unisys (Mar 2003 - Dec 2005)}}\label{unisys-mar-2003---dec-2005}

\begin{itemize}
\tightlist
\item
  Performed security assessments, penetration tests, and risk
  assessments for clients in the Financial Services, Health Care,
  Manufacturing, and Public sectors.
\item
  Wrote and presented post-engagement reports to clients and provided
  guidance for addressing findings in line with business objectives.
\item
  Developed labor models and project materials to support pre-sales and
  standardize engagement delivery across the security practice.
\item
  Developed application penetration test capabilities and assessment
  framework for other consultants within the practice.
\item
  Directed team activities for large assessments and security
  infrastructure implementation projects.
\end{itemize}

\subparagraph{Accomplishments}\label{accomplishments-3}

\begin{itemize}
\tightlist
\item
  Was written up in article for
  \href{http://www.informationweek.com/hack-in-progress/d/d-id/1020652}{InformationWeek}
\end{itemize}

\subsubsection{Senior Staff, Security
Engineering}\label{senior-staff-security-engineering}

\subparagraph{\texorpdfstring{\emph{Zurich Global Assets} (Jun 2002 -
Feb
2003)}{Zurich Global Assets (Jun 2002 - Feb 2003)}}\label{zurich-global-assets-jun-2002---feb-2003}

\begin{itemize}
\tightlist
\item
  Administered local IDS, Firewall, and UNIX systems.
\item
  Acted as ZGA divisional representative at Zurich Financial Services
  Global Information Technology Services activities.
\item
  Performed security assessments on ZGA and ZFS infrastructure.
\item
  Performed local security monitoring.
\item
  Lead global security monitoring team (Dublin, Zurich, Schaumberg, New
  York, Los Angeles) across ZFS divisions.
\item
  Lead the global PKI implementation team
\item
  Lead design and implementation for Security and Network Operations
  Center for ZGA infrastructure.
\end{itemize}

\subsubsection{Technical Services
Director}\label{technical-services-director}

\subparagraph{\texorpdfstring{\emph{ThruPoint} (Oct 1999 - Jun
2002)}{ThruPoint (Oct 1999 - Jun 2002)}}\label{thrupoint-oct-1999---jun-2002}

\begin{itemize}
\tightlist
\item
  Performed security assessment, penetration test, infrastructure
  design, and infrastructure implementation projects for clients in
  Financial Services and Media sectors.
\item
  Served as final internal point of escalation for all security
  consulting technical matters across the company.
\item
  Directed security projects for large engagements.
\item
  Provided staff skills development assistance for other security
  consultants.
\item
  Design, build, and support in-house security testing lab environment.
\end{itemize}

\subsubsection{Security Consultant}\label{security-consultant-1}

\subparagraph{\texorpdfstring{\emph{Security Industries Automation
Corporation (SIAC)} (Oct 1998 - Sep
1999)}{Security Industries Automation Corporation (SIAC) (Oct 1998 - Sep 1999)}}\label{security-industries-automation-corporation-siac-oct-1998---sep-1999}

\begin{itemize}
\tightlist
\item
  Did first shift firewall operations for Gauntlet firewalls on the
  internal perimeter networks.
\item
  Performed start-of-day and end-of-day procedures to ensure continuity
  of operations for second and third shifts.
\item
  Did requirements analysis for business requests and implemented
  subsequent infrastructure changes.
\item
  Performed UNIX system administration tasks to support maintenance
  activities.
\item
  Participated in Y2K readiness preparations for NYSE security
  infrastructure.
\end{itemize}

\subsubsection{Security Consultant}\label{security-consultant-2}

\subparagraph{\texorpdfstring{\emph{Interactive Futures} (May 1997 - Sep
1998)}{Interactive Futures (May 1997 - Sep 1998)}}\label{interactive-futures-may-1997---sep-1998}

\begin{itemize}
\tightlist
\item
  Performed security assessments for clients in the Media, Legal, and
  non-profit sector.
\item
  Designed and implemented CheckPoint and Gauntlet firewalls for VAR
  customers.
\item
  Designed and implemented Sun Solaris/SPARC systems for VAR customers.
\item
  Supported pre-sales discovery and developed written responses to RFP
  solicitations.
\end{itemize}

\subsection{Certifications}\label{certifications}

\begin{itemize}
\tightlist
\item
  Completion of Advanced Training - Mercedes AMG Driving Academy (2015)
\item
  Leadership Skills for Managers Certificate Program - University of
  Texas at Austin Professional Development Center (2011)
\item
  Advanced SCADA Security - Idaho National Laboratory National SCADA
  Test Bed (2008)
\item
  Certified SCADA Security Architect - Digital Bond, Inc. (2006)
\end{itemize}

\subsection{Courses}\label{courses}

\begin{itemize}
\tightlist
\item
  SANS - Microsoft Windows Security (SANS-505)
\item
  SANS - Reverse-engineering Malware (SANS-610)
\item
  SANS - PowerShell (SANS-537)
\item
  SANS - Identifying and Removing Malware (SANS-537)
\item
  HP Enterprise - ArcSight ESM 6.5 Security Administrator and Analyst
  (HPE-00924200)
\end{itemize}

\subsection{Awards}\label{awards}

\begin{itemize}
\tightlist
\item
  ERCOT - Team Player Award (Mar 2016)
\item
  Mercedes AMG Driving Academy - 1st place Team Autocross (Jun 2015)
\item
  ERCOT - Core Value Award for Expertise (Apr 2014)
\item
  ERCOT - Team Player Award (Apr 2014)
\item
  ERCOT - Exceptional Performer Award (Jan 2014)
\item
  ERCOT - Certificate of Recognition: Principal (Dec 2012)
\item
  ERCOT - Team Player Award (Jul 2011)
\item
  Idaho National Laboratory NSTB Advanced SCADA Security Training - Team
  Captain and Winning Team (Nov 2008)
\end{itemize}

\subsection{Skills}\label{skills}

\begin{itemize}
\item
  \textbf{Security}\\
  ArcSight ESM, ArcSight Logger, ArcSight Connectors, ArcSight
  Management Center, Bro IDS, McAfee Network Security Platform,
  SourceFire IPS, Suricata IDS, RSA Security Analytics, Netwitness,
  Carbon Black Protection (Bit9 Parity), AppLocker, SILK, Argus,
  Gigamon, SELinux
\item
  \textbf{DF-IR}\\
  Volatility Framework, plaso, log2timeline, sleuthkit, foremost,
  Memoryze, EnCase, F-Response, Carbon Black Response, Soltra Edge,
  STIX, CybOx, TAXII, OpenIOC, Cuckoo Sandbox, McAfee Advanced Threat
  Detection
\item
  \textbf{Vulnerability Management}\\
  Rapid7 Nexpose, RedSeal, Tenable SecurityCenter, MetaSploit Pro,
  PhishMe, OpenSCAP, SCAP, OVAL, XCCDF
\item
  \textbf{Crypto}\\
  HashiCorip Vault, Microsoft Certificate Services, cfssl, OpenSSL,
  PKCS11, TPM, x509, PKI
\item
  \textbf{Config Automation}\\
  packer, Chef, Ansible, Consul, ActiveDirectory Group Policy
\item
  \textbf{Languages}\\
  Ruby, Python, R, Shell/Bash, PowerShell, Go/golang, Scala, JavaScript
\item
  \textbf{Workflow}\\
  JIRA, SharePoint, Confluence, HipChat, rundeck, Stash, Bitbucket, git
\item
  \textbf{Testing}\\
  jenkins, TravisCI, Bamboo, selenium, cucumber, rspec, serverspec,
  brakeman, rubocop, capybara
\item
  \textbf{Data Repositories}\\
  MySQL/MariaDB, PostgreSQL, Cassandra, ElasticSearch, InfluxDB, OSISoft
  PI System, Apache ZooKeeper
\item
  \textbf{Data Pipeline}\\
  Apache Kafka, RabbitMQ, Logstash, Pentaho Data Integration, Flume,
  Sqoop, Avro, Parquet
\item
  \textbf{Monitoring}\\
  Telegraf, Kapacitor, Zabbix, Nagios, CollectD, DiamonD, StatsD,
  Graphite, jolokia, jmxtrans
\item
  \textbf{Web}\\
  Apache HTTPD, nginx, varnish cache, squid, haproxy, traefik
\item
  \textbf{Virtualization}\\
  VMWare ESX, Docker, QEMU, KVM, OpenStack, Vagrant, AWS EC2
\item
  \textbf{Analysis-Visualization}\\
  Jupyter, Rstudio, Apache Spark, Tableau, Pig, pandas, scikit-learn,
  shiny, grafana, kibana
\item
  \textbf{Compliance}\\
  NERC CIP, SSAE16, NIST SP800-53, NIST CyberSecurity Framework
\item
  \textbf{Operating Systems}\\
  CentOS/RHEL 5-7, Windows Server 2008/2012, macOS, OpenBSD, FreeBSD
\item
  \textbf{Network}\\
  Cisco IOS, Arista EOS, openvswitch, ISC BIND, AWS Route53, InfoBlox
  DDI, wireshark
\item
  \textbf{Storage}\\
  ceph, minio, OpenStack Swift, AWS S3
\end{itemize}

\end{document}
